\section{Introduction}
\subsection{Purpose of the system}
The purpose of the calendar system is to make a calendar system for a workplace, capable of sharing entries and organizing meetings etc.
The system is intended to be used in a workplace environment, where people know each other, or at least are acquainted in some way. Thus the program has no need for contact lists and blocking of people, since it is used by people working together, to organize meetings etc.
\subsection{Design goals}
\flushleft{\textbf{Usability:} The system should be easy to learn, since it is can be used by a wide array of people with different backgrounds and different levels of expertise, it should be hard to learn since it will not be a small group of experts using the system.}
\flushleft{\textbf{Fault tolerance:}The system should be fault tolerant to loss of connectivity with the calendar server. Since the centralised server might die, it would be a problem if every user completely loses access to their calendar on such an occasion.}
\flushleft{The system should use a low amount of bandwidth. Since the users most likely will have a client running all the time while working, it should require a low amount of bandwidth as to not slow down the entire network.}
\flushleft{The client part of the system should be  compatible with older windows versions.since the system is to be used in a work environment, where the upgrade time may vary a lot, it should be compatible with all the commonly used versions of windows, to make it usable by most companies.}
\subsection{Definitions, acronyms, and abbreviations}
\subsection{References}
\subsection{Overview}